%!TEX TS-program = xelatex
\documentclass[]{chandan-cv}
\usepackage{hyperref}
\hypersetup{
  colorlinks, linkcolor=red
}

\begin{document}
\header{Kunal}{Chandan}
       {Computer Engineering Student}


% In the aside, each new line forces a line break
\begin{aside}
  \section{About}
    11 Four Winds Dr #14
    M3J 1K7
    Toronto, ON
    ~
    \href{mailto:kunalthechandan@gmail.com}{kunalthechandan –@gmail.com}
    \href{https://kunalchandan.github.io}{kunalchandan.github.io}
    Cell: (647)-785-1313
  \section{Languages}
    Bilingual English \& Hindi
    Limited French
  \section{Programming}
    Java
    Python
    OpenCV-
    Octave/MATLAB
    PsychToolbox-
    HTML \& JavaScript
    LaTeX
\end{aside}

\section{Interests}

I take heavy interest in computer science, mainly in statistical analysis and machine learning. I first learned to program with Java in 2015, since then I have been improving my skills now I have some experience with Keras, Octave, and OpenCV. I also lead Northview's FIRST robotics team and the programming team.

\section{Education}

\begin{entrylist}
  \entry
    {2018–2023}
    {Expected Computer Engineering Degree{\normalfont}}
    {University of Waterloo}
    {Honours Computer Engineering Co-op. Starting September of 2018}
  \entry
    {2014–2018}
    {Ontario Secondary School Diploma{\normalfont}}
    {Northview Heights Secondary School}
    {Specialist High Skills Major; Information Computer Tech. (SHSM - ICT)\\
    Honours in Math, Science and Technology (HMST)}
\end{entrylist}

\section{Experience}

\begin{entrylist}
  \entry
    {July '17–Curr.}
    {Elder Lab, York University}
    {Research Internship.}
    {\emph{Computer Vision, Machine Learning, and Psychophysics}\\-Learning to design neural networks for application in various projects i.e. Traffic tracking, hockey puck tracking\\-Writing machine learning algorithms in Java, and Python using Keras and Tensorflow\\-Writing scripts using Python and OpenCV for data augmentation and various libraries for data visualization and interpretation\\-MATLAB and PsychToolbox for designing psychophysics experiments\\-Designing methods to gather crowd-sourced data with Amazon MTurk}
  \entry
    {July–Aug '17}
    {Camp NAORCA, City of Toronto}
    {Camp Counsellor.}
    {\emph{Voted Rookie of the year}; outdoor youth summer camp}
  \entry
    {2017-2018}
    {FIRST Team 6632, Supreme Robotics}
    {Build Executive}
    {Lead and coordinated Supreme Robotics' build team}
  \entry
    {Jan '18}
    {Northview Heights Secondary School}
    {Lead Programming Mentor}
    {Mentored Northview's Co-Ed and All-girls programming teams}
  \entry
    {2016-2018}
    {Private Tutoring}
    {Math \& Science Tutor}
    {Tutored children in math and science at local libraries.}
\end{entrylist}

\section{Applications}

\begin{entrylist}
  \entry
    {2017–Curr.}
    {Personal Website}
    {\href{https://kunalchandan.github.io}{kunalchandan.github.io}}
    {Various JavaScript applets, web-toys, and 3D Rendering done with Blender}
  \entry
    {2017–Curr.}
    {Various Psychophysics Experiments}
    {Research Internship related work}
    {Designed and programmed psychophysics experiments similar to current research in the Elder Lab}
\end{entrylist}

\newpage

\section{Other Extra-Curriculars}

\begin{entrylist}
  \entry
    {2014–Curr.}
    {Academic Clubs}
    {}
    { -Programming Club Founder
    \\-Biology Club Executive
    \\-Physics Club Member
    \\-Math Team Member
    \\-DECA Chapter Executive
    \\-SHSM-ICT President
    \\-FIRST Robotics Build Executive}
  \entry
    {2014–Curr.}
    {Sports Clubs}
    {}
    { -Cross Country Coach/Member
    \\-Badminton Member
    \\-Water Polo Member
    \\-Track \& Field Coach/Member}
\end{entrylist}

\section{Awards}

\begin{entrylist}
  \entry
    {2014–Curr.}
    {Academic Awards}
    {}
    { -Co-op Award for Outstanding Achievement - Grade 12
    \\-Business Award - Grade 9 \& 10
    \\-Honour Roll - All Semesters
    \\-University of Toronto National Biology Competition Scholar Award - Grade 12
    \\-CCC Junior 1st place Northview - Grade 11
    \\-ECOO Round 2 Finalist - Grade 11
    \\-Toronto Finalist for Office Skills Competition - Grade 10
    \\-Toronto Finalist for Robotics and Control Systems - Grade 11}
  \entry
    {2014–Curr.}
    {Athletic Awards}
    {}
    { -Bronze Medallion for TDSSAA - Cross Country
    \\-Silver Medallion for TDSSAA - Track \& Field}
\end{entrylist}

\end{document}
