%!TEX TS-program = xelatex
\documentclass[]{chandan-cv}
\begin{document}
\header{Kunal}{Chandan}
       {Computer Engineering Student}

% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    11 Four Winds Dr #14
    M3J 1K7
    Toronto, ON
    ~
    \href{mailto:kunalthechandan@gmail.com}{kunalthechandan@gmail.com}
    \href{https://kunalchandan.github.io}{https://kunalchandan.github.io}
  \section{languages}
    English \& Hindi
  \section{programming}
    Java
    Python
    HTML \& JavaScript
\end{aside}

\section{interests}

I take heavy interest in computer science, mainly specializing in machine learning. I have some experience with Tensorflow, Keras, and OpenCV. I also regularly participate in FIRST robotics and programming competitions.

\section{education}
\begin{entrylist}

\end{entrylist}
\begin{entrylist}
  \entry
    {2018-Beyond}
    {B.Eng or B.Sc {\normalfont University of ___}}
    {University in Ontario somewhere!}
  \entry
    {2014-2018}
    {High school Diploma}
    {Northview Heights Secondary School}
    {Specialist High Skills Major in Information Computer Technology (SHSM - ICT) \\
    Honours in Math, Science and Technology (HMST) }
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {02–07 2009}
    {LIP6/CNRS, Paris}
    {Research Internship.}
    {\emph{Visualization of complex networks.}}
  \entry
    {06–08 2008}
    {ISCPIF/CNRS, Paris}
    {Research Internship.}
    {\emph{Diffusion in the Blogosphere. Happy Flu.}}
  \entry
    {06–08 2007}
    {LIP6/CNRS, Paris}
    {Research Internship.}
    {\emph{Kernels in real world networks.}}
  \entry
    {07–08 2005}
    {\href{http://www.kelkoo.com}{Kelkoo.com}}
    {Summer job.}
    {\emph{Creation of a keyword generator for Google Adwords.}}
  \entry
    {07–08 2004}
    {\href{http://www.monsieurprix.com}{MonsieurPrix.com}}
    {Summer job.}
    {\emph{Development of an e-commerce product indexation spider.}}
\end{entrylist}

\section{applications}

\begin{entrylist}
  \entry
    {2012}
    {Who did I forget ?}
    {\href{http://whodidiforget.com}{whodidiforget.com}}
    {Guest list recommendation for Facebook events based on friends already attending the event.}
  \entry
    {2011}
    {Fellows}
    {\href{http://fellows-exp.com}{fellows-exp.com}}
    {Automatic community detection among Facebook Friends in order to validate the \emph{cohesion} measure, creation of friend lists.}
\end{entrylist}

\section{publications}

\end{document}
